---
title: "Formative Assessment 3"
author: "Vera Aguila"
date: "2024-02-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Question 2

2.  A binary communication channel carries data as one of two sets of signals denoted by 0 and 1. Owing to noise, a transmitted 0 is sometimes received as a 1, and a transmitted 1 is sometimes received as a 0. For a given channel, it can be assumed that a transmitted 0 is correctly received with probability 0.95, and a transmitted 1 is correctly received with probability 0.75. Also, 70% of all messages are transmitted as a 0. If a signal is sent, determine the probability that:
<br>
Given when event:
<br>  0 is received = R~0~ = 0.95
<br>  1 is received = R~1~ = 0.75
<br>  0 is transmitted = T~0~ = 0.7
<br>  1 is transmitted = T~1~ = 0.3
  
*(a) a 1 was received;
  <br>  P(R~1~) = P(T~0~) P(R~1~|T~0~) + P(T~1~) P(R~1~|T~1~)
  <br><br>   P(T~0~) = 0.7                <br>    P(T~1~) = 0.3
  <br>       P(R~1~|T~0~) = 1 - 0.95 = 0.05    <br>   P(R~1~|T~1~) = 0.75
<br>
```{r q2.1}
# 0 is received = reZ = 0.95
# 1 is received = reO = 0.75
# 0 is transmitted = trZ = 0.7
# 1 is transmitted = trO = 0.3

reZ <- 0.95
reO <- 0.75
trZ <- 0.7
trO <- 0.3

prob1 <- (trZ*(1-reZ))+(trO*reO)
cat("Probability of receiving 1 (P(R1)):", prob1, "\n")
```
<br>
<br>
*(b) a 1 was transmitted given than a 1 was received. 
P(T~1~|R~1~) = \( \frac{P(T~1~)P(R~1~|T~1~)}{P(R~1~)} \)
<br><br> P(T~1~) = 0.3        
     P(R~1~) = 0.26
<br>     P(R~1~|T~1~) = 0.75
<br>
```{r q2.2}
prob2 <- (trO*reO)/(prob1)
cat("Probability of receiving 1 when 1 was transmitted: ", prob2, "\n")
```
<br>
<br>


### Question 7

7.  There are three employees working at an IT company: Jane, Amy, and Ava, doing 10%, 30%, and 60% of the programming, respectively. 8% of Jane’s work, 5% of Amy’s work, and just 1% of Ava‘s work is in error. What is the overall percentage of error? If a program is found with an error, who is the most likely person to have written it? <br>
<br>    Given:
<br>    work of Jane = W~J~ = 0.1
<br>    work of Amy = W~Am~ = 0.3
<br>    work of Ava = W~Av~ = 0.6
<br>    Error:
<br>    error of Jane = E~J~ = 0.08
<br>    error of Amy = E~Am~ = 0.05
<br>    error of Ava = E~Av~ = 0.01
<br><br>
<br>    *(a) overall percentage of error
<br>    E = (J ∩ E) ∪ (Am ∩ E) ∪ (Av ∩ E)
<br>    P(E) = P(J)P(E|J) + P(Am)P(E|Am) + P(Av)P(E|Av) 
<br><br> P(J) = 0.1
<br>    P(E|J) = 0.08
<br>    P(Am) = 0.3
<br>    P(E|Am) = 0.05
<br>    P(Av) = 0.6
<br>    P(E|Av) = 0.01
<br>
```{r q7.1}
# work of Jane = WJ = 0.1
# work of Amy = WAm = 0.3
# work of Ava = WAv = 0.6
# error of Jane = EJ = 0.08
# error of Amy = EAm = 0.05
# error of Ava = EAv = 0.01
# E = overall error

WJ = 0.1
WAm = 0.3
WAv = 0.6
EJ = 0.08
EAm = 0.05
EAv = 0.01

E <- (WJ*EJ) + (WAm*EAm) + (WAv*EAv)
E <- E*100
cat("The overall percentage of error:", E, "%\n")
```
<br><br>
*(b) If a program is found with an error, who is the most likely person to have written it?
<br>
<br>**Percentage error of Jane:**
<br> P(J|E) = \( \frac{P(W~J~)P(E|W~J~)}{P(E)} \)
<br> P(W~J~) = 0.1
<br> P(E|W~J~) = 0.08
<br> P(E) = 0.029
<br>
```{r q7.2}
E <- E/100
prob3 <- (WJ*EJ)/E
prob3 <- prob3*100
cat("The percentage of error:", prob3,"%\n")
```
<br>
<br>**Percentage error of Amy:**
<br> P(Am|E) = \( \frac{P(W~Am~)P(E|W~Am~)}{P(E)} \)
<br> P(W~Am~) = 0.3
<br> P(E|W~JAm~) = 0.05
<br> P(E) = 0.029
<br>
```{r q7.3}
prob4 <- (WAm*EAm)/E
prob4 <- prob4*100
cat("The percentage of error:", prob4,"%\n")
```
<br>
<br>**Percentage error of Ava:**
<br> P(Av|E) = \( \frac{P(W~Av~)P(E|W~Av~)}{P(E)} \)
<br> P(W~Av~) = 0.6
<br> P(E|W~JAv~) = 0.01
<br> P(E) = 0.029
<br>
```{r q7.4}
prob5 <- (WAv*EAv)/E
prob5 <- prob5*100
cat("The percentage of error:", prob5,"%\n")
```
<br>
<br>
Since the highest percentage of error is 51.72%, the most likely person to have written it is Amy.
<br><br>

